DSSynth: An Automated Synthesis Tool of Digital \\ Controllers for Physical Plants via MATLAB Toolbox

### 2017-06-04 ase2017/paper.tex
added UAV illustrative example

\title{DSSynth: An Automated Synthesis Tool of Digital Controllers \\ for Physical Plants via MATLAB Toolbox}

@@

\textcolor{red}{Lennon, can you please use an illustrative example related to UAV?}

To illustrate the \tool's usage, Fig.~\ref{toolbox-usage} shows the 
synthesis for a physical plant defined in Eq.(~\ref{equation_plant}) 
using the transfer-function representation, where ``num'' and ``den'' 
represent the numerator $A(z)$ and denominator $B(z)$, respectively.
%
\begin{equation}
\label{equation_plant}
H(z)=\frac{B(z)}{A(z)}=\frac{-0.06875z^{2}}{z^2-1.696z+0.7089}.
\end{equation}
%
\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
>> num = [-0.06875 0 0];
>> den = [1.0000 -1.696 0.7089];
>> system = tf(num,den,0.002);
>> y = synthesize(system,8,8,1,-1);
>> SYNTHESIS SUCCESSFUL
>> y = (-0.9983z^2 + 0.09587z + 0.1926)/(z^2+0.5665+0.75);
\end{lstlisting}
\vspace{-0.2cm}
\caption{Synthesis of a digital controller for the physical plant defined in Eq.(~\ref{equation_plant}) in MATLAB, with a fixed-point format  $\left\langle 8,8\right\rangle$.}
\label{toolbox-usage}
\end{figure}
%
In Fig.~\ref{toolbox-usage}, the value returned in variable $y$ represents 
the synthesized stable digital controller. In order to validate and reproduce 
the stability of the digital system composed by the physical plant defined in Eq.(~\ref{equation_plant}) 
and the digital controller represented by $y$, the user can invoke the step response using the 
command \texttt{dstep}, and then observe that the plotted graph shows a stable digital system, 
as shown in Fig.~\ref{step-response}.
%
\begin{figure}[ht]
  \includegraphics[width=0.5\textwidth]{step-response.eps}
  \caption{Step response for the Eq.~\eqref{equation_plant} describing a stable system.}
  \label{step-response}
\end{figure}

>>>>

\title{DSSynth: An Automated Synthesis Tool of Digital \\ Controllers for Physical Plants via MATLAB Toolbox}

@@

To illustrate the \tool's usage, Fig.~\ref{toolbox-usage} shows the 
synthesis for a physical plant defined in Eq.(~\ref{equation_plant}),
which represents a UAV a quadcopter system, whose model was described by Bouabdallah {\it et al.}~\cite{bouabdallah}. The physical plant in Eq.(~\ref{equation_plant}) is represented using the transfer-function format, where ``num'' and ``den'' 
represent the numerator $A(z)$ and denominator $B(z)$, respectively.
%
\begin{equation}
\label{equation_plant}
H(z)=\frac{B(z)}{A(z)}=\frac{-0.06875z^{2}}{z^2-1.696z+0.7089}.
\end{equation}
%
\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
>> num = [-0.06875 0 0];
>> den = [1.0000 -1.696 0.7089];
>> system = tf(num,den,0.002);
>> y = synthesize(system,8,8,1,-1);
>> SYNTHESIS SUCCESSFUL
>> y = (-0.9983z^2 + 0.09587z + 0.1926)/(z^2+0.5665+0.75);
\end{lstlisting}
\vspace{-0.2cm}
\caption{Synthesis of a digital controller for the physical plant defined in Eq.(~\ref{equation_plant}) in MATLAB, with a fixed-point format  $\left\langle 8,8\right\rangle$.}
\label{toolbox-usage}
\end{figure}
%
In Fig.~\ref{toolbox-usage}, the value returned in variable $y$ represents 
the synthesized stable digital controller. In order to validate and reproduce 
the stability of the digital system composed by the physical plant defined in Eq.(~\ref{equation_plant}) 
and the digital controller represented by $y$, the user can invoke the step response using the 
command \texttt{dstep}, and then observe that the plotted graph shows a stable digital system, 
as shown in Fig.~\ref{step-response}.
%
\begin{figure}[ht]
  \includegraphics[width=0.5\textwidth]{step-response.eps}
  \caption{Step response for the Eq.~\eqref{equation_plant} describing a stable system.}
  \label{step-response}
\end{figure}
